Assignment 5

### 2015-02-24 rmtw/a5/latex8.tex
Small changes YOLO

Mattsson et al. \cite{mattsson2009linking} discuss the correlation between MDSD and software architecture. The idea that MDSD is benefitial if done right is presented, and one important factor brought up is the need of automatic enforcment of architectural rules \cite{mattsson2009linking}. If this has to be done manually, it will become a bottleneck in large MDSD projects \cite{mattsson2009linking}.

>>>>

Mattsson et al. \cite{mattsson2009linking} discuss the correlation between MDSD and software architecture. The idea that MDSD is beneficial if performed correctly is presented, and one important factor discussed is the need of automatic enforcement of architectural rules \cite{mattsson2009linking}. If this has to be performed manually, it will become a bottleneck in large MDSD projects \cite{mattsson2009linking}.
